Statistical methods for relative quantification of post-translational modifications in global proteomics experiments

### 2021-09-09 supplementary/ptm_sm.tex
Updated sections and graphs of supplementary

In this study, the correlation between the autophagy gene Atg16L1 and killing of virulent Shigella flexneri (S.flexneri) was assessed. It was discovered that the loss of Atg16L1 in macrophages enhanced the killing of S.flexneri. Multiplex proteomics was used to quantify the abundance of total protein, phosphorylation, and ubiquitination in wild type (WT) and ATG16L1-deficient (cKO) bone marrow macrophages, uninfected and uninfected with S.flexneri. The abundance of total protein and post-translation modifications were quantified at three time points, uninfected, early infections, and late infection. Quantifying the total protein along with the post-translational modifications allows us to adjust for changes in total protein and see the true impact of the site specific modifications.

>>>>

In this study, the correlation between the autophagy gene Atg16L1 and killing of virulent Shigella flexneri (S.flexneri) was assessed. It was discovered that the loss of Atg16L1 in macrophages enhanced the killing of S.flexneri. Multiplex proteomics was used to quantify the abundance of total protein, phosphorylation, and ubiquitination in wild type (WT) and ATG16L1-deficient (cKO) bone marrow macrophages, uninfected and uninfected with S.flexneri. The abundance of total protein and post-translation modifications were quantified at three time points, uninfected, early infection (45-60 minutes), and late infection (3-3.5 hours). Quantifying the total protein along with the post-translational modifications allows us to adjust for changes in total protein and see the true impact of the site specific modifications.
